---
title: "2019 Field design"
output: NULL
author: "Semra Palali Delen"
date: 01-25-2021
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```

# Nomenclature for the field design

In 2019, we used the same design, but just one check.

1. Two blocks (North, South), low and high N plot in each block. North is lowland and South is highland.
2. 4 split-plots per block by height and flowering time (tall/early, tall/late, short/early, short/late)
split plots, subdivided into 3 incomplete split-plot-blocks
3x8 = 24 subplots per split plot block

## Dimensions:

1. Plot: 120 ft x 240 ft
2. subplot 20 ft x 5 ft, 288 subplots per plot and 72 subplots per split plot
17.5 feet would give us 20 foot plots with 30 inches between varieties.

----------------

# Seed sources:
1. Schnable Lab Chile 2019
2. Schachtman and Yang Lab Chile 2018 remaining


```{r}
fb <- read.csv("data/fb2019_JY_282_4plots_havelock_final.csv")
```

### Two blocks
```{r}
fb$block <- "B1"
fb[fb$row > 3000,]$block <- "B2"

fb$nitrogen <- "+N"
fb[fb$row > 2000 & fb$row < 4000, ]$nitrogen <- "-N"

```



### four split-blocks per block

```{r}
fb$sb <- NA
fb$reminder1 <- fb$row %% 1000 
fb$reminder2 <- fb$reminder1 %% 100 
fb[fb$reminder1 < 300 & fb$reminder2 <= 42,]$sb <- "sb1"
fb[fb$reminder1 < 300 & fb$reminder2 > 42,]$sb <- "sb2"
fb[fb$reminder1 > 300 & fb$reminder2 <= 42,]$sb <- "sb3"
fb[fb$reminder1 > 300 & fb$reminder2 > 42,]$sb <- "sb4"

table(fb$sb)
```

### split-plot-blocks
```{r}
fb$spb <- NA
fb[fb$sb == "sb1" & fb$reminder2 <= 14,]$spb <- "spb1"
fb[fb$sb == "sb1" & fb$reminder2 > 14 & fb$reminder2 <= 28,]$spb <- "spb2"
fb[fb$sb == "sb1" & fb$reminder2 > 28 & fb$reminder2 <= 42,]$spb <- "spb3"

fb[fb$sb == "sb2" & fb$reminder2 > 42 & fb$reminder2 <= 56,]$spb <- "spb1"
fb[fb$sb == "sb2" & fb$reminder2 > 56 & fb$reminder2 <= 70,]$spb <- "spb2"
fb[fb$sb == "sb2" & fb$reminder2 > 70 & fb$reminder2 <= 84,]$spb <- "spb3"

fb[fb$sb == "sb3" & fb$reminder2 <= 14,]$spb <- "spb1"
fb[fb$sb == "sb3" & fb$reminder2 > 14 & fb$reminder2 <= 28,]$spb <- "spb2"
fb[fb$sb == "sb3" & fb$reminder2 > 28 & fb$reminder2 <= 42,]$spb <- "spb3"

fb[fb$sb == "sb4" & fb$reminder2 > 42 & fb$reminder2 <= 56,]$spb <- "spb1"
fb[fb$sb == "sb4" & fb$reminder2 > 56 & fb$reminder2 <= 70,]$spb <- "spb2"
fb[fb$sb == "sb4" & fb$reminder2 > 70 & fb$reminder2 <= 84,]$spb <- "spb3"

table(fb$spb)
table(subset(fb, sb=="sb4")$spb)

write.table(fb, "cache/fb2019_meta.csv", sep=",", row.names = FALSE, quote=FALSE)
```

### Test

3000s is a low nitrogen field. find the sb4 and spb1 in plot 3000s,
- should be > 3343
- should contain two row of "checks"
```{r}
test1 <- subset(fb, block == "B2" & nitrogen =="-N" & sb=="sb4" & spb=="spb1")
sum(test1$genotype == "check")
```


After planting, the empty plots (no gemination) were replaced with checks.



```{r}
fb <- read.csv("cache/fb2019_meta.csv")

### file withplots replaced with checks:
ch <- read.csv("data/CRRI_2019_Field_Book_Christine.csv")

fb2 <- merge(fb[, -4:-5], ch, by.x="row", by.y="Row")

write.table(fb2[, -13:-14], "cache/fb2019_meta_replaced_check.csv", sep=",", row.names = FALSE, quote=FALSE)
```