---
title: "2018 Field design"
output: NULL
author: "Semra Palali Delen"
date: 01-25-2021
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```

# Nomenclature for the field design

In 2018, we used the same design with 2 checks

1. Two blocks (East, West), low and high N plot in each block.
2. 4 split-plots per block by height and flowering time (tall/early, tall/late, short/early, short/late)
split plots, subdivided into 3 incomplete split-plot-blocks
3x8 = 24 subplots per split plot block

## Dimensions:

1. Plot: 120 ft x 240 ft
2. subplot 20 ft x 5 ft, 288 subplots per plot and 72 subplots per split plot
17.5 feet would give us 20 foot plots with 30 inches between varieties.

----------------

# Seed sources:


```{r}
fb18 <- read.csv("../data/fb2018_JY_282_4plots.csv")
#View(fb18)
```

### Two blocks
```{r}
fb18$block <- "B1"
fb18[fb18$row > 3000,]$block <- "B2"

fb18$nitrogen <- "+N"
fb18[fb18$row > 2000 & fb18$row < 4000, ]$nitrogen <- "-N"

```



### four split-blocks per block

```{r}
fb18$sb <- NA
fb18$reminder1 <- fb18$row %% 1000 
fb18$reminder2 <- fb18$reminder1 %% 100 
fb18[fb18$reminder1 < 300 & fb18$reminder2 <= 48,]$sb <- "sb1"
fb18[fb18$reminder1 < 300 & fb18$reminder2 > 48,]$sb <- "sb2"
fb18[fb18$reminder1 > 300 & fb18$reminder2 <= 48,]$sb <- "sb3"
fb18[fb18$reminder1 > 300 & fb18$reminder2 > 48,]$sb <- "sb4"

table(fb18$sb)
```

### split-plot-blocks
```{r}
fb18$spb <- NA
fb18[fb18$sb == "sb1" & fb18$reminder2 <= 16,]$spb <- "spb1"
fb18[fb18$sb == "sb1" & fb18$reminder2 > 16 & fb18$reminder2 <= 32,]$spb <- "spb2"
fb18[fb18$sb == "sb1" & fb18$reminder2 > 32 & fb18$reminder2 <= 48,]$spb <- "spb3"

fb18[fb18$sb == "sb2" & fb18$reminder2 > 48 & fb18$reminder2 <= 64,]$spb <- "spb1"
fb18[fb18$sb == "sb2" & fb18$reminder2 > 64 & fb18$reminder2 <= 80,]$spb <- "spb2"
fb18[fb18$sb == "sb2" & fb18$reminder2 > 80 & fb18$reminder2 <= 96,]$spb <- "spb3"

fb18[fb18$sb == "sb3" & fb18$reminder2 <= 16,]$spb <- "spb1"
fb18[fb18$sb == "sb3" & fb18$reminder2 > 16 & fb18$reminder2 <= 32,]$spb <- "spb2"
fb18[fb18$sb == "sb3" & fb18$reminder2 > 32 & fb18$reminder2 <= 48,]$spb <- "spb3"

fb18[fb18$sb == "sb4" & fb18$reminder2 > 48 & fb18$reminder2 <= 64,]$spb <- "spb1"
fb18[fb18$sb == "sb4" & fb18$reminder2 > 64 & fb18$reminder2 <= 80,]$spb <- "spb2"
fb18[fb18$sb == "sb4" & fb18$reminder2 > 80 & fb18$reminder2 <= 96,]$spb <- "spb3"

table(fb18$spb)
table(subset(fb18, sb=="sb4")$spb)



fb18$Rep <- "1"
fb18[fb18$row > 3000,]$Rep <- "2"

write.table(fb18[, -16:-17], "../cache/fb2018_meta.csv", sep=",", row.names = FALSE, quote=FALSE)

fb18_meta <- read.csv("../cache/fb2018_meta.csv")
View(fb18_meta)

#nrow(fb18)

```

